Spectral Lags in Very High Energy Emission of Gamma Ray Bursts

### 2013-10-20 gammaRays.tex
Fixed definition of \eta

To understand the observed spectral lag, lets explore geometry of the jet. First of all, lets make some assumptions:
\begin{enumerate}
\item{Time $t = 0$, a spherical shell of plasma is emitted. The center is called the central engine.}
\item{The shell points propagate with a constant velocity $v \sim 1$, so at the time $t$ the radius of the shall is $v t$.}
\item{Each point of the shell is an isotropic radiator in its reference frame.}
\item{
	The radiation intensity is a function of the radiator position and the radiation frequency:
	\begin{equation}
		\eta\left(r,\theta,\omega\right) = 
		\frac{\eta_0}{1 + \left(\frac{r}{r_0}\right)^n}
		\exp\left(
			-\left(\frac{\theta}{\theta_0}\right)^2
			\left(\frac{\omega}{\omega_0}\right)^{-2k}
		\right)
		\left(\frac{\omega}{\omega_0}\right)^\alpha
	\end{equation}
	$\eta$ is a number of particles emitted per volume per frequency. It is a function of the distance $r$ from the central engine, of the off-axis angle $\theta$, and of the radiation frequency $\omega$.
}
\end{enumerate}

@@

\subsection{Total energy}
\subsection{Spectrum}
\subsection{Distribution}
\subsection{Case study}

>>>>

To understand the observed spectral lag, lets explore geometry of the jet. First of all, lets make some assumptions:
\begin{enumerate}
\item{Time $t = 0$, a spherical shell of plasma is emitted. The center is called the central engine.}
\item{The shell points propagate with a constant velocity $v \sim 1$, so at the time $t$ the radius of the shall is $v t$.}
\item{Each point of the shell is an isotropic radiator in its reference frame.}
\item{
	The radiation intensity is a function of the radiator position and the radiation frequency:
	\begin{equation}
		\eta\left(r,\theta,\omega\right) = 
		\frac{\eta_0}{1 + \left(\frac{r}{r_0}\right)^n}
		\exp\left(
			-\left(\frac{\theta}{\theta_0}\right)^2
			\left(\frac{\omega}{\omega_0}\right)^{-2k}
		\right)
		\left(\frac{\omega}{\omega_0}\right)^\alpha
	\end{equation}
	$\eta$ is a number of particles emitted per volume per solid angle per frequency. It is a function of the distance $r$ from the central engine, of the off-axis angle $\theta$, and of the radiation frequency $\omega$.
}
\end{enumerate}

@@

\subsection{Total energy}

The first test is to compute the total energy radiated from the burst, and to ensure that it doesn't exceed the mass of the star from which the burst originated.

However, the largest contribution to the total energy in our model is due to unobservable low-energy photons. Moreover, the total energy integral diverges on low energies as we will see later. This divergence is understandable, since our model is only valid only for large energy photons. Still, we have to ensure that the total energy of radiated high energy photons is low enough.

To do that, we have to modify the expression for the radiation intensity, to cut off all the radiators with frequencies outside the $\left(\omega_1, \omega_2\right)$ interval:
\begin{equation}
	\eta_{\omega_1}^{\omega_2}\left(r,\theta,\omega\right) = \begin{cases}
		0 & \text{if } \omega < \omega_1 \\
		\eta\left(r,\theta,\omega\right) & \text{if } \omega_1 < \omega < \omega_2 \\
		0 & \text{if } \omega_2 < \omega
	\end{cases}
\end{equation}

\subsection{Spectrum}
\subsection{Distribution}
\subsection{Case study}
